Unsupervised embedding of trajectories captures the latent structure of mobility

### 2020-10-19 paper/current/main.tex
added figshare record to data availability statement

\subsection*{Data Availability}
The U.S. airline itinerary dataset can be found at \url{https://www.transtats.bts.gov/DataIndex.asp}. 
In case of the South Korean accommodation reservation dataset, due to the nature of the dataset, participants of this study did not agree for their data to be shared publicly.
Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;
however, we have made available all metadata and trained neural embeddings available at XYZ.

>>>>

\subsection*{Data Availability}
The U.S. airline itinerary dataset can be found at \url{https://www.transtats.bts.gov/DataIndex.asp}. 
In case of the South Korean accommodation reservation dataset, due to the nature of the dataset, participants of this study did not agree for their data to be shared publicly.
Due to its proprietary nature, the global scientific mobility dataset, sourced from the Web of Science, cannot be provided;
however, metadata and trained neural embeddings have been published at \url{https://doi.org/10.6084/m9.figshare.13072790.v1}
